### 2022-04-23 paper/ase22/experiment.tex
exp setup

First, \tool generates sentences and its label by empirical reasoning
derived from \lc statements. Therefore, we meaure acceptibility of the
testcases by verifying the relevancy between sentence and label, and
between sentence and its \lc. The RQ~\ref{rq:one} thereby is answered
by verifying the quality of generated testcases. In this work, we
conduct manual study and measure the correlation of human labeled
testcases and \tool labeled testcases. Second, the amount of NLP model
component executed during testing is a critical measurement for
assessing quality of software testing. A high software coverage
results in higher chances of unidentified bugs in the NLP model. On
the other hand, limited distribution only represents narrow portion of
real world covering limited execution paths in a NLP model. It leads
to detect bugs within the restricted execution paths.  Therefore,
testcases more equivalent to real world represents more generalized
distribution, and it results in high coverage of the NLP model.
Accordingly, the ability of testcases to produce high portion of model
coverage needs to be measured. We answer the RQ~\ref{rq:three}
measuring neural coverage of the neural NLP model according to the
measurements. In addition to the detection of bugs in the model,
explaination of the bugs is also important stage of debugging and
repairing the model. Therefore, we anwer RQ~\ref{rq:four} by showing
usefulness of \tool by analyzing the NLP model based on \tool and
finding root of the bug.

\subsection{Experiment Setup}
We conduct practical experiments and show the effectiveness of
\tool.

\subsubsection{Manual study}
We sample set of test cases and corresponding \lc randomly sampled
from seed sentences and expanded sentences from \tool.  Subjects are
also provided with the sampled testcases. Each subject is asked for
scoring relevancy between the linguistic capability of the
sentences. The scores range from 1 to 5 representing strongly not
relevant to strongly relevant respectively. Additionally, the subject
scores the relevancy between sentences and their sentiment labels. The
scores also range from 1 to 5, and they represent strongly negative to
strongly positive respectively. In this work, we collect manual study
scores from {} subjects attended. From the collected scores, we
measure the following metrics:

\begin{enumerate}[label=\textbf{Metrics}]
\item \label{mm:one} Reported bugs
\item \label{mm:two} Incorrect inputs
\item \label{mm:three} Label Inconsistency
%% \item \label{rq:three}: How effective is our new test case generation
%%   using \cfg expansion? % ablation study
\end{enumerate}

The metrics used for this study

>>>>

First, \tool generates sentences and its label by empirical reasoning
derived from \lc statements. Therefore, we meaure acceptibility of the
testcases by verifying the relevancy between sentence and label, and
between sentence and its \lc. The RQ~\ref{rq:one} thereby is answered
by verifying the quality of generated testcases. In this work, we
conduct manual study and measure the correlation of human labeled
testcases and \tool labeled testcases. Second, the amount of NLP model
component executed during testing is a critical measurement for
assessing quality of software testing. A high software coverage
results in higher chances of unidentified bugs in the NLP model. On
the other hand, limited distribution only represents narrow portion of
real world covering limited execution behaviors in a NLP model. It leads
to detect bugs within the restricted execution behaviors.  Therefore,
testcases more equivalent to real world represents more generalized
distribution, and it results in high coverage of the NLP model.
Accordingly, the ability of testcases to produce high portion of model
coverage needs to be measured. We answer the RQ~\ref{rq:three}
measuring neural coverage of the neural NLP model according to the
measurements. In addition to the detection of bugs in the model,
explaination of the bugs is also important stage of debugging and
repairing the model. Therefore, we anwer RQ~\ref{rq:three} by showing
usefulness of \tool by analyzing the NLP model based on \tool and
finding root of the bug.

\subsection{Experiment Setup}
We conduct practical experiments and show the effectiveness of
\tool.
\subsubsection*{\textbf{Manual Study}}
We sample set of test cases and corresponding \lc randomly sampled
from seed sentences and expanded sentences from \tool.  Subjects are
also provided with the sampled testcases. Each subject is asked for
scoring relevancy between the linguistic capability of the
sentences. The score is discrete and it ranges from 1 to 5
representing ``strongly not relevant'' to ``strongly relevant''
respectively. Additionally, the subject scores the relevancy between
sentences and their sentiment labels. The score is also discreate and
ranges from 1 to 5. It represents ``strongly negative'' to ``strongly
positive'' respectively. In this work, we collect manual study scores
from 8 subjects attended. From the collected scores, we measure the
following metrics:

\begin{eqnarray}
  &Reported\:bugs &=\sum_{i} \delta(label_{S^2LCT}!=pred_{model}) \label{metric:rb}\\
  &Incorrect\:inputs &= \sum_{i} \delta(pred_{model}!=label_{human}) \label{metric:ii}\\
  %% &Label\:inconsistency &= \sum_{i} \delta(label_{S^2LCT}!=label_{human}) \label{metric:li}
\end{eqnarray}

The metrics represents the number of data instance that its label
assigned from are different between \tool and its model prediction
(eq~\ref{metric:rb}) and between the model prediction and human
(eq~\ref{metric:ii}). We show the correspondonce between \tool and
human by computing the precision and recall from the reported bugs and
incorrect inputs.
%% and between \tool and human (eq~\ref{metric:li}).

\subsubsection*{\textbf{Model Coverage}}
We implement DeepXplore to measure the NLP model
coverage~\cite{pei2017deepxplore}. \Dxp is the first efficient
whitebox testing framework for large-scale \dl systems. It introduces
neuron coverage of a set of test inputs as the ratio of the number of
unique activated neurons and the total number of neurons in input \dl
system. In this experiment, we compute the neuron coverage of a test
cases from \tool and \Cklst on the fine-tuned \sa model of
\bertsamodel and compare the coverage between \tool and \Cklst.
